---
title: "index"
author: "RajD"
date: "December 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

#### Explore dataset- mtcars

```{r cars}
data(cars)
# View(mtcars)
head(mtcars)
tail(mtcars)
str(mtcars)
#mtcars$mpg
#table(mtcars$mpg)
```

#### Including Plots

```{r boxplot}
ggplot(mtcars, aes(x=factor(am), y=mpg)) + geom_boxplot()
# Why do we need to turn am into a factor: because ggplot2 prefers the x-axis of a boxplot to be a factor- that is, a variable that can take one of a finite number of categories as its values- rather than a numeric variable like 0 or 1. Then we put the type of graph, which in this case is geom_boxplot
```

#### Compare 2 variables
t-test examines whether a numeric variable differed between two categories.

```{r compare}
tTest = t.test(mpg ~ am, data=mtcars)
tTest
```

#### Correlation
we might be interested in testing whether a car's weight affects fuel efficiency.

```{r correlation}
ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point()
```

you can see a negative relationship: a higher weight means a higher miles per gallon and therefore a lower fuel efficiency in. This makes intuitive sense: a heavier car requires more fuel.


The simplest way to test for a relationship between two variables is with a correlation test. This can be done with the cor.test function:

```{r}
corrTest = cor.test(mtcars$mpg, mtcars$wt)
corrTest
```

The smaller the p-value, the more significant the correlation, so here we can be very confident that a correlation exists.


