---
title: "Linear Regression"
author: "RajD"
date: "December 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

#### Fitting the Line and looking at summary, Also looking at co-efficients.

```{r slrFit}
regr = lm(mpg ~ wt, mtcars)
summary(regr)

coeff = coef(summary(regr))
coeff

coeff[ ,1]
```

#### Prediction using predict() function

```{r prediction}
predict(regr)
```

But these predictions aren't that useful to us, as we already have the actual gas mileage of each.

What if we wanted to predict the gas mileage of a car that has a weight of, say, 4500 pounds?

```{r}
37.2851 + (-5.3445) * 4.5
```

This predicts a fuel efficiency of 13.2 miles per gallon for 4.5 thousands of pounds.

There is a shortcut for producing this value from the fit, using the predict function. First we create a data frame containing the predictors we wish to use. In this case, imagine we had a new car that weighed 4500 pounds:

```{r new data}
newcars = data.frame(wt = c(4.5, 4.2, 4.1, 4.32, 4.4, 4.65, 5.5, 5.2))
predict(regr, newcars)
```

#### Plotting

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) + geom_point() + geom_smooth(method = "lm")
```

The grey area shown is the uncertainty in the fit: it's a 95% confidence interval of where the true trend line could be.
